---
title: "p8105_hw5_mgg2153"
author: "mggn"
date: "11/16/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1, as discussed in the live session from 11/10/2020

Read in the data.

```{r}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



```{r, error = TRUE}
city_prop_test = function(df) {
  
  n_unsovled ...
  n_total ... 
  
  prop.test(.....)
  
}
homicide_df = 
  read_csv("data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") %>% 
  nest(data = resolved)
```


## Problem 2

First, I'll start by creating a dataframe using the list.files command:

```{r}
goal_spaghetti = 
list.files(path = "./hw5_data", full.names=FALSE)%>%
  tibble::enframe(name = NULL)

#am I doing this right? lol we shall see
```

It appears that this created a dataframe with no variables?
LOL because I was typing data_hw5 instead of hw5_data kill me

```{r}
goal_spaghetti_df =
  goal_spaghetti %>%
  mutate(
    data = map(value, ~read_csv(str_c("./hw5_data/", .x)))
  ) %>%
  unnest(cols = data) %>%
  separate(value, into=c("arm", "participant_id"))%>%
  mutate(participant_id = str_replace(participant_id, ".csv", ""))%>%
  pivot_longer(
   week_1:week_8,
   names_to = "week",
   names_prefix = "week_", 
   values_to = "obs_value"
  )
 

```

Now we get to the goal of this problem: spaghetti! (plots)

```{r}
goal_spaghetti_df %>%
  mutate(
    arm = recode(arm,
      con = "Control",
      exp = "Experimental"
    )
  ) %>%
  ggplot(aes(x = week, y = obs_value, group = participant_id, color = participant_id))+
  geom_point()+
  geom_path()+
  labs(
   x = "Week number",
   y = "Observation value",
   title = "Observations on each subject over time by treatment arm",
   caption = "Spaghetti plot"
  )+
  facet_grid(.~arm)+
  theme_bw()+
  theme(legend.position = "none", plot.title = element_text(size = 11))

```
Looks like the control group has relatively "stable" measures versus the experimental group seems so have 
a trend that is increasing over time

## Problem 3 lol

```{r}
set.seed(1)

sim_power = function(n = 30, mu, sigma = 5) {
  
  sim_data = tibble(
    x = rnorm(n = n, mean = mu, sd = sigma)
  )
  
  sim_data %>%
    summarize(
      mu = mean(x),
      sigma = sd(x)
    )
  
 
    sim_data %>%
      t.test() %>%
      broom::tidy() %>% 
      select(estimate, p.value)

}
```

```{r}
#generate 5000 models

output = rerun(5000, sim_power(30, 0, 5)) %>%
  bind_rows()

```

```{r}
#repeat for mu = 1-6

sim_results = 
  tibble(
    mu = c(0, 1, 2, 3, 4, 5, 6)
  )%>%
  mutate(
    output_list = map(.x = mu, ~rerun(5000, sim_power(mu = .x))),
    output_df = map(output_list, bind_rows)
  )%>%
  unnest(output_df) %>%
  select(-output_list)

head(sim_results)
  
```

```{r}
reject_plot =
  sim_results %>%
  group_by(mu) %>%
  count(p.value < 0.05)%>%
  mutate(
    power = n/sum(n)
  )%>%
  janitor::clean_names()%>% #p_value becomes p_value_0_05 and is boolean
  filter(p_value_0_05 == TRUE) %>%
  ggplot(aes(x = mu, y = power))+
  geom_point(color = "magenta")+
  geom_smooth(se = FALSE)

```
